Coherent Hyper-Raman Four Wave Mixing Spectroscopies

### 2024-06-11 paper.tex
added fayer ref

Most quantitative methods in an n$^{th}$ order CMDS experiment are used to extract $\chi^{(n)}$ values for comparing the relative strength of nonlinear processes in different media. \cite{Zhu87, RN351, RN345}
The recorded $\chi^{(n)}$ values provide insight into how microscopic quantities ($\vec{\mu}, \alpha_{ij}, \beta_{ijk}$) impact nonlinear output.
To our knowledge, only 2D-IR spectroscopy has taken advantage of orientationally averaged $\chi^{(3)}$ values to extract transition moments.\cite{Grechko2012}
Previous treatments did not consider using quantitative analysis in SIVE to measure $\beta_{ijk}$ values from SIVE spectra.
It is thus useful to investigate how a simple treatment of orientational averaging can extract $\beta_{ijk}$ from a $\chi^{(3)}_{IJKL}$ expression.

>>>>

Most quantitative methods in an n$^{th}$ order CMDS experiment are used to extract $\chi^{(n)}$ values for comparing the relative strength of nonlinear processes in different media. \cite{Zhu87, RN351, RN345}
The recorded $\chi^{(n)}$ values provide insight into how microscopic quantities ($\vec{\mu}, \alpha_{ij}, \beta_{ijk}$) impact nonlinear output.
To our knowledge, only 2D-IR spectroscopy has taken advantage of orientationally averaged $\chi^{(3)}$ values to extract transition moments. \cite{Moilanen2009, Grechko2012}
Previous treatments did not consider using quantitative analysis in SIVE to measure $\beta_{ijk}$ values from SIVE spectra.
It is thus useful to investigate how a simple treatment of orientational averaging can extract $\beta_{ijk}$ from a $\chi^{(3)}_{IJKL}$ expression.
